Reference label transfer from the fetal full reference (Cao et al.) for `r params$sample_id`

### 2024-08-29 analyses/cell-type-wilms-tumor-06/notebook_template/02a_label-transfer_fetal_full_reference_Cao.Rmd
Expand timeout for reference download
Try debug RunAzimuth

    # Calculate percent mitochondrial genes if the query contains genes
    # matching the regular expression "^MT-"
    if (any(grepl(pattern = '^MT-', x = rownames(x = query)))) {
      query <- PercentageFeatureSet(
        object = query,
        pattern = '^MT-',
        col.name = 'percent.mt',
        assay = assay
      )
    }
    # Find anchors between query and reference
    anchors <- FindTransferAnchors(
      reference = reference,
      query = query,
      k.filter =  NA,
      reference.neighbors = "refdr.annoy.neighbors",
      reference.assay = "refAssay",
      query.assay = assay,
      reference.reduction = "refDR",
      normalization.method = "SCT",
      features = rownames(Loadings(reference[["refDR"]])),
      dims = 1:dims,
      n.trees = n.trees,
      mapping.score.k = mapping.score.k,
      verbose = verbose
    )
    # Transferred labels are in metadata columns named "predicted.*"
    # The maximum prediction score is in a metadata column named "predicted.*.score"
    # The prediction scores for each class are in an assay named "prediction.score.*"
    # The imputed assay is named "impADT" if computed
    refdata <- lapply(X = annotation.levels, function(x) {
      reference[[x, drop = TRUE]]
    })
    names(x = refdata) <- annotation.levels

@@

    query <- TransferData(
      reference = reference,
      query = query,
      query.assay = assay,
      dims = 1:dims,
      anchorset = anchors,
      refdata = refdata,
      n.trees = 20,
      store.weights = TRUE,
      k.weight = k.weight,
      verbose = verbose
    )
    # Calculate the embeddings of the query data on the reference SPCA
    query <- IntegrateEmbeddings(
      anchorset = anchors,
      reference = reference,
      query = query,
      query.assay = assay,
      reductions = "pcaproject",
      reuse.weights.matrix = TRUE,
      verbose = verbose
    )
    # Calculate the query neighbors in the reference
    # with respect to the integrated embeddings
    query[["query_ref.nn"]] <- FindNeighbors(
      object = Embeddings(reference[["refDR"]]),
      query = Embeddings(query[["integrated_dr"]]),
      return.neighbor = TRUE,
      l2.norm = TRUE,
      verbose = verbose
    )
    # The reference used in the app is downsampled compared to the reference on which
    # the UMAP model was computed. This step, using the helper function NNTransform,
    # corrects the Neighbors to account for the downsampling.
    query <- Azimuth:::NNTransform(
      object = query,
      meta.data = reference[[]]
    )
    # Project the query to the reference UMAP.
    query[[umap.name]] <- RunUMAP(
      object = query[["query_ref.nn"]],
      reduction.model = reference[["refUMAP"]],
      reduction.key = 'UMAP_',
      verbose = verbose
    )

    # Calculate mapping score and add to metadata
    query <- AddMetaData(
      object = query,
      metadata = MappingScore(anchors = anchors, ndim = dims,  ksmooth = 80),
      col.name = "mapping.score"
    )

@@

We install and load the reference using `Azimuth`.
```{r path_to_reference}
#Check the names of the Azimuth available data and reference
AvailableData()

>>>>

    # Calculate percent mitochondrial genes if the query contains genes
    # matching the regular expression "^MT-"
    if (any(grepl(pattern = '^MT-', x = rownames(x = query)))) {
      query <- PercentageFeatureSet(
        object = query,
        pattern = '^MT-',
        col.name = 'percent.mt',
        assay = assay
      )
    }
    # Find anchors between query and reference
    anchors <- FindTransferAnchors(
      reference = reference,
      query = query,
      k.filter =  NA,
      reference.neighbors = "refdr.annoy.neighbors",
      reference.assay = "refAssay",
      query.assay = assay,
      reference.reduction = "refDR",
      normalization.method = "SCT",
      features = rownames(Loadings(reference[["refDR"]])),
      dims = 1:dims,
      n.trees = n.trees,
      mapping.score.k = mapping.score.k,
      verbose = verbose
    )

    print("FindTransferAnchors done")
    # Transferred labels are in metadata columns named "predicted.*"
    # The maximum prediction score is in a metadata column named "predicted.*.score"
    # The prediction scores for each class are in an assay named "prediction.score.*"
    # The imputed assay is named "impADT" if computed
    refdata <- lapply(X = annotation.levels, function(x) {
      reference[[x, drop = TRUE]]
    })
    names(x = refdata) <- annotation.levels

@@

    query <- TransferData(
      reference = reference,
      query = query,
      query.assay = assay,
      dims = 1:dims,
      anchorset = anchors,
      refdata = refdata,
      n.trees = 20,
      store.weights = TRUE,
      k.weight = k.weight,
      verbose = verbose
    )
        print("TransferData done")

    # Calculate the embeddings of the query data on the reference SPCA
    query <- IntegrateEmbeddings(
      anchorset = anchors,
      reference = reference,
      query = query,
      query.assay = assay,
      reductions = "pcaproject",
      reuse.weights.matrix = TRUE,
      verbose = verbose
    )
            print("IntegrateEmbeddings done")

    # Calculate the query neighbors in the reference
    # with respect to the integrated embeddings
    query[["query_ref.nn"]] <- FindNeighbors(
      object = Embeddings(reference[["refDR"]]),
      query = Embeddings(query[["integrated_dr"]]),
      return.neighbor = TRUE,
      l2.norm = TRUE,
      verbose = verbose
    )
                print("FindNeighbors done")

    # The reference used in the app is downsampled compared to the reference on which
    # the UMAP model was computed. This step, using the helper function NNTransform,
    # corrects the Neighbors to account for the downsampling.
    query <- Azimuth:::NNTransform(
      object = query,
      meta.data = reference[[]]
    )

                    print("NNTransform done")

    # Project the query to the reference UMAP.
    query[[umap.name]] <- RunUMAP(
      object = query[["query_ref.nn"]],
      reduction.model = reference[["refUMAP"]],
      reduction.key = 'UMAP_',
      verbose = verbose
    )
                        print("RunUMAP done")

    # Calculate mapping score and add to metadata
  #  query <- AddMetaData(
   #   object = query,
    #  metadata = MappingScore(anchors = anchors, ndim = dims,  ksmooth = mapping.score.k, kanchors = (k.weight+1)),
     # col.name = "mapping.score"
    #)

    return(query)

@@

We install and load the reference using `Azimuth`.
```{r path_to_reference}
options(timeout=600)

#Check the names of the Azimuth available data and reference
AvailableData()
